curatedMetagenomicData

### 2020-01-28 manuscript_NS_MRD.Rmd
updated

plot_abundance.ak = function(pseq.subset, title_text,
                         Facet = "Genus", Color = "Phylum"){
 # Arbitrary subset, based on Phylum, for plotting
 p1f = subset_taxa(pseq.subset, Genus %in% c("Akkermansia"))
 mphyseq = psmelt(p1f)
 mphyseq <- subset(mphyseq, Abundance > 0)
 p <- ggplot(data = mphyseq, mapping = aes_string(x = "mnd",y = "Abundance")) +
   geom_violin(fill = NA) +
   geom_point(size = 1, alpha = 0.3,
              position = position_jitter(width = 0.3)) + scale_y_log10()+
   theme(legend.position="none") + scale_colour_manual(values = wes_palette(glob_theme)) + theme_classic() + xlab('MND DALYs')
 #library(rms)
#fita <- lrm(mnd ~ gender + log(Abundance) + bmi_group + age_category, data =mphyseq)
#fita <- lrm(mnd ~ gender + log(Abundance) , data =mphyseq)
#fita <- lrm(mnd ~ gender + log(Abundance) + bmi_group, data =mphyseq)

>>>>

plot_abundance.ak = function(pseq.subset, title_text,
                         Facet = "Genus", Color = "Phylum"){
 # Arbitrary subset, based on Phylum, for plotting
 p1f = subset_taxa(pseq.subset, Genus %in% c("Akkermansia"))
 mphyseq = psmelt(p1f)
 mphyseq <- subset(mphyseq, Abundance > 0)

  mnd <- levels(mphyseq$mnd) # get the variables
  # Make a pairwise list that we want to compare.
  mnd.pairs <- combn(seq_along(mnd), 2, simplify = FALSE, FUN = function(i)mnd[i])
  mnd.pairs <- list( c("LOW","MEDIUM"), c("HIGH","LOW"), c("MEDIUM","HIGH"))

  # Compare differences in Shannon index between mnd group of the study subjects
  mphyseq$mnd <- factor(mphyseq$mnd, levels = c("LOW","MEDIUM","HIGH"),  exclude = "NA")
  # on to the graphs!!!
  print("The basic alpha diversity analysis has been completed")

 p <- ggplot(data = mphyseq, mapping = aes_string(x = "mnd",y = "Abundance")) +
   geom_violin(fill = NA) +
   geom_point(size = 1, alpha = 0.3,
              position = position_jitter(width = 0.3)) + scale_y_log10()+
   theme(legend.position="none") + scale_colour_manual(values = wes_palette(glob_theme)) + stat_compare_means(comparisons = mnd.pairs) + theme_classic() + xlab('MND DALYs')
 #library(rms)
#fita <- lrm(mnd ~ gender + log(Abundance) + bmi_group + age_category, data =mphyseq)
#fita <- lrm(mnd ~ gender + log(Abundance) , data =mphyseq)
#fita <- lrm(mnd ~ gender + log(Abundance) + bmi_group, data =mphyseq)
